The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
fix double space
nobs results

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength varied in winter layers at low number of observations, becoming stable
at ~75 observations and was consistently weak in summer layers (Figure
\@ref(fig:nobs)a). Layer relevance in winter layers increased between ~10 m and
~100 m observations, remaining stable with additional observations (Figure
\@ref(fig:nobs)b). Like coarse landcover resolution (Figure \@ref(fig:lcres)),
low numbers of observations were not sufficient for capturing individuals in all
contexts and therefore layer similarity could not be calculated below ~30
observations for forest, approximately ~80 observations for open (Figure
\@ref(fig:nobs)c). Layer similarity was not possible to calculate for forage
layers because there were no connected individuals in summer forage. Once
sufficient observations were obtained, layer similarity was relatively stable
for forest and open layers. Connective redundancy increased dramatically between
~10 m and ~50 m observations before stabilizing with all new observations
included (Figure \@ref(fig:nobs)d). Given the observed trend of these multilayer
metrics stabilizing after a certain number of observations are included, the
results suggest this sensitivity method could be useful for determining the
number of observations necessary for sufficiently describing social dynamics
across contexts.

>>>>

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength was consistently weak in summer layers but varied in winter layers at
low number of observations, becoming stable at ~75 observations (Figure
\@ref(fig:nobs)a). Layer relevance in the summer was consistently low, but
winter layers increased between approximately 10  and 100  observations,
remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
coarse landcover resolution (Figure 4), low numbers of observations were not
sufficient for capturing individuals in all contexts and therefore layer
similarity could not be calculated below ~30 observations for forest,
approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
similarity was not possible to calculate for forage layers because there were no
connected individuals in summer forage. Once sufficient observations were
obtained, layer similarity showed some variability with increasing numbers of
observations for forest and was relatively stable in open layers. Connective
redundancy increased dramatically between ~10 and ~50 observations before
stabilizing with additional observations included (Figure \@ref(fig:nobs)d).
Given the observed trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing social dynamics across contexts.
